Denotational Semantics of General Payment Primitives, and Its Payment System

### 2022-09-27 packages/spec-haskell/yellowpaper/Paper.tex
concluide draft of Payment Execution Environment

\paragraph{}

A payment system can be solely defined by these components:

@@

\paragraph{}

@@

\paragraph{}

Here are some examples how that could work:

@@

The purpose of a payment execution environment is to perform the actual payment primitives taking into account their
conditions, timing and order.

@@

>>>>

\paragraph{Payment system}

It can be solely defined by these components:

@@

\paragraph{Modernization}

@@

\paragraph{Components of Context}

Here are some possible components of context, and how they work:

@@

The purpose of a payment execution environment is to perform the actual payment primitives, where their computation
interface, parallel evaluation strategies and payment system solvency are defined.

@@

\subsection{Payment System Solvency}
